---
title: "Metering Configuration Review"
output: html_notebook
---

```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(scales)
```
Disclaimer:  While every attempt has been made to ensure the accuracy of the material in this script, 
221B Ltd makes no warranty as to the accuracy, completeness or usefulness for any particular purpose 
of the material in this script; and they accept no liability for errors of fact or opinion in this 
script, whether or not due to negligence on the part of any party.

Table Names
```{r}
meter_names <- c("RegionID", "NetworkRegion", "NSP", "Count", "Residential", "PriceCategoryCode", "flow_content_poa")
```

Import data from Electricity Authority of New Zealand (EMI web portal) 
```{r}
#Update the filename to indicate the latest dataset.  
#Also update filename reference in each chart
meter_configuration <- NULL
meter_configuration <- read_csv("https://www.emi.ea.govt.nz/Retail/Datasets/MarketStructure/ICPandMeteringDetails/20191231_MeteringConfigurationsInclDistributionPriceCatCode.csv",
                                col_types = "cccnlcc",
                                col_names = meter_names,
                                skip = 1)
```

Factorise the data as factors to simplify reporting
```{r}
meter_configuration$NetworkRegion <- as.factor(meter_configuration$NetworkRegion)
meter_configuration$PriceCategoryCode <- as.factor(meter_configuration$PriceCategoryCode)
```

separate individual meter registers into separate rows
```{r}
meter_configuration <- meter_configuration %>% 
                       separate_rows(flow_content_poa, sep = ' ')
```

Split into Flow Direction (X= Load, I= Generation), Register Content Code and Period of Availability
```{r}
meter_configuration <- meter_configuration %>% 
                       separate(flow_content_poa, 
                                c("flow", "content", "poa"), 
                                sep = '-'
                                )
```

Set period of availability as an integer
```{r}
meter_configuration$poa <- as.factor(meter_configuration$poa)
sorted_poa <- paste(sort(as.integer(levels(meter_configuration$poa))))
meter_configuration$poa <- factor(meter_configuration$poa, levels = sorted_poa)
```

Aggregate results per Region, Flow, Register Content and Period of Avaialbilty (dropping the Distributor Price Category Code)
```{r}
meter_configuration <- meter_configuration %>% 
                       group_by(RegionID, NetworkRegion, flow, content, poa) %>% 
                       summarise(register_count = sum(Count)) %>%
                       mutate(register_detail = paste(flow, content, poa, sep = "-"))

meter_configuration %>% ungroup() %>%
                        mutate(NetworkRegion = fct_reorder(NetworkRegion, RegionID)) 
```
Split out the registers into groups for detailed review
```{r}
nhh_registers <- NULL
nhh_registers <- meter_configuration %>% 
                     select(RegionID, NetworkRegion, flow, content, poa, register_count) %>%
                     group_by(RegionID, NetworkRegion, content, flow) %>%
                     filter(!content %in% c("7302", "7304", "7306", "7056")) %>%
                     summarise(register_count = sum(register_count))

generation_issues <- NULL
generation_issues <- meter_configuration %>% 
                     select(RegionID, NetworkRegion, flow, content,register_count) %>%
                     group_by(RegionID, NetworkRegion, content) %>%
                     filter(!content %in% c("7302", "7304", "7306", "7056","RH", "AH", "EG"), 
                     flow == "I") %>%
                     summarise(register_count = sum(register_count))

generationflow_issues <- NULL
generationflow_issues <- meter_configuration %>% 
                     select(RegionID, NetworkRegion, flow, content,register_count) %>%
                     group_by(RegionID, NetworkRegion, content) %>%
                     filter(content =="EG", 
                     flow == "X") %>%
                     summarise(register_count = sum(register_count))

generationpoa_issues <- NULL
generationpoa_issues <- meter_configuration %>% 
                     select(RegionID, NetworkRegion, flow, content, poa, register_count) %>%
                     group_by(RegionID, NetworkRegion, poa, content) %>%
                     filter(content == "EG", 
                     flow == "I",
                     !poa == 24) %>%
                     summarise(register_count = sum(register_count))

uncontrolled_issues <- NULL
uncontrolled_issues <- meter_configuration %>% 
                       ungroup() %>%
                       select(RegionID, NetworkRegion, flow, content, poa, register_count) %>% 
                       group_by(RegionID, NetworkRegion, content, poa, flow) %>%
                       filter(content == "UN", 
                       flow == "X",
                       !poa == "24") %>%
                       summarise(register_count = sum(register_count))

inclusive_issues <- NULL
inclusive_issues <- meter_configuration %>% 
                       ungroup() %>%
                       select(RegionID, NetworkRegion, flow, content, poa, register_count) %>% 
                       group_by(RegionID, NetworkRegion, content, poa, flow) %>%
                       filter(content == "IN") %>%
                       summarise(register_count = sum(register_count))

controlled_issues <- NULL
controlled_issues <- meter_configuration %>% 
                       ungroup() %>%
                       select(RegionID, NetworkRegion, flow, content, poa, register_count) %>% 
                       group_by(RegionID, NetworkRegion, content, poa, flow) %>%
                       filter(content == "CN") %>%
                       summarise(register_count = sum(register_count))

diurnal_issues <- NULL
diurnal_issues <- meter_configuration %>% 
                     select(RegionID, NetworkRegion, flow, content,register_count) %>%
                     group_by(RegionID, NetworkRegion, content) %>%
                     filter(content %in% c("D", "N", "DC", "NC", "DUN", "NUN"), 
                     flow == "X") %>%
                     summarise(register_count = sum(register_count))

poa24_issues <- NULL
poa24_issues <- meter_configuration %>% 
                     select(RegionID, NetworkRegion, flow, content, poa, register_count) %>%
                     group_by(RegionID, NetworkRegion, content) %>%
                     filter(!content %in% c("UN", "IN", "INEM", "EG", "RH", "S", "W", "WE","WD", "AD", "AH", "KD", "7302", "7304", "7306", "7056"), 
                     flow == "X",
                     poa == "24") %>%
                     summarise(register_count = sum(register_count))

```

Chart total of each register content code per network
```{r}
options(scipen=1000000)
ggplot(nhh_registers, aes(fct_reorder(NetworkRegion, desc(RegionID)), register_count, fill = content)) +
  geom_col(colour = "white", width = 1) +
  scale_y_continuous(label = comma) +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0),
        legend.position = "right"
        ) +
  labs(title = "NHH Registers per Content Code", 
       subtitle = "20191231_MeteringConfigurationsInclDistributionPriceCatCode.csv",
       fill = "Register Content Code", 
       caption = "Data source: www.emi.ea.govt.nz provided by the Electricity Authority (New Zealand)") +
  xlab("Network Reporting Region") + 
  ylab("Count of NHH Registers") 
```

Chart Uncontrolled meter register content codes without 24 hours of availability
```{r}
ggplot(uncontrolled_issues, aes(fct_reorder(NetworkRegion, desc(RegionID)), register_count, fill = poa)) +
  geom_col(position = "stack") +
  coord_flip() +
  labs(title = "Uncontrolled Registers Excluding 24 Hours",
       subtitle = "20191231_MeteringConfigurationsInclDistributionPriceCatCode.csv",
       caption = "Data source: www.emi.ea.govt.nz provided by the Electricity Authority (New Zealand)") +
  xlab("Network Region") + 
  ylab("Number of Registers per Network") +
  labs(fill = "Hours")
```

Chart the Inclusive 24 hour registers (should be UN24 or INxx)
```{r}
ggplot(inclusive_issues %>% filter(poa %in% c(0,24)), aes(fct_reorder(NetworkRegion, desc(RegionID)), register_count, fill = poa)) +
  geom_col(position = "stack", colour = "white", width = 1) +
  scale_y_continuous(label = comma) +
  coord_flip() +
  labs(title = "Discrete Inclusive 24 hour Registers",
       subtitle = "20191231_MeteringConfigurationsInclDistributionPriceCatCode.csv",
       caption = "Data source: www.emi.ea.govt.nz provided by the Electricity Authority (New Zealand)") +
  xlab("Network Region") + 
  ylab("Number of Registers per Network") +
  labs(fill = "Hours")
```

Chart the number of controlled registers per period of availabilty
```{r}
ggplot(controlled_issues, aes(fct_reorder(NetworkRegion, desc(RegionID)), register_count, fill = poa)) +
  geom_col(position = "stack", colour = "white", width = 1) +
  scale_y_continuous(label = comma) +
  coord_flip() +
  labs(title = "Discrete Controlled Registers",
       subtitle = "20191231_MeteringConfigurationsInclDistributionPriceCatCode.csv",
       caption = "Data source: www.emi.ea.govt.nz provided by the Electricity Authority (New Zealand)") +
  xlab("Network Region") + 
  ylab("Number of Registers per Network") +
  labs(fill = "Hours")
```

Plot the Generation (I Flow) register content codes without EG register content code
```{r}
ggplot(generation_issues, aes(fct_reorder(NetworkRegion, desc(RegionID)), register_count, fill = content)) +
  geom_col(position = "stack") +
  coord_flip() +
  labs(title = "Generation non 'EG' Register Content Codes",
       subtitle = "20191231_MeteringConfigurationsInclDistributionPriceCatCode.csv",
       caption = "Data source: www.emi.ea.govt.nz provided by the Electricity Authority (New Zealand)") +
  xlab("Network Region") + 
  ylab("Number of Registers per Network") +
  labs(fill = "Content Code")
```
Chart the Generation EG register content codes with Load (flow direction X)
```{r}
ggplot(generationflow_issues, aes(fct_reorder(NetworkRegion, desc(RegionID)), register_count, fill = content)) +
  geom_col(position = "stack") +
  coord_flip() +
  labs(title = "Load Flow 'EG' Register Content Codes",
       subtitle = "20191231_MeteringConfigurationsInclDistributionPriceCatCode.csv",
       caption = "Data source: www.emi.ea.govt.nz provided by the Electricity Authority (New Zealand)") +
  xlab("Network Region") + 
  ylab("Number of Registers per Network") +
  labs(fill = "Content Code")
```

Plot the Generation EG register content code registers without 24 hours available
```{r}
ggplot(generationpoa_issues, aes(fct_reorder(NetworkRegion, desc(RegionID)), register_count, fill = poa)) +
  geom_col(position = "stack") +
  coord_flip() +
  labs(title = "Generation non 24 Hour Register Content Codes",
       subtitle = "20191231_MeteringConfigurationsInclDistributionPriceCatCode.csv",
       caption = "Data source: www.emi.ea.govt.nz provided by the Electricity Authority (New Zealand)") +
  xlab("Network Region") + 
  ylab("Number of Registers per Network") +
  labs(fill = "Hours")
```

Chart the day night registers 
```{r}
ggplot(diurnal_issues, aes(fct_reorder(NetworkRegion, desc(RegionID)), register_count, fill = content)) +
  geom_col(position = "stack") +
  coord_flip() +
  labs(title = "Day Night Register Content Codes",
       subtitle = "20191231_MeteringConfigurationsInclDistributionPriceCatCode.csv",
       caption = "Data source: www.emi.ea.govt.nz provided by the Electricity Authority (New Zealand)") +
  xlab("Network Region") + 
  ylab("Number of Registers per Network") +
  labs(fill = "Content Code")
```

Chart load flow register content codes with 24 hours available but not UN24.
```{r}
ggplot(poa24_issues, aes(fct_reorder(NetworkRegion, desc(RegionID)), register_count, fill = content)) +
  geom_col(position = "stack") +
  coord_flip() +
  labs(title = "Incorrect 24 Hour Register Content Codes",
       subtitle = "20191231_MeteringConfigurationsInclDistributionPriceCatCode.csv",
       caption = "Data source: www.emi.ea.govt.nz provided by the Electricity Authority (New Zealand)") +
  xlab("Network Region") + 
  ylab("Number of Registers per Network") +
  labs(fill = "Content Code")
```
